Demography and selection since maize domestication

### 2015-05-18 manuscript.tex
a bit of intro

\documentclass{pnastwo}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
\usepackage{hyperref}
\newcommand{\jri}[1]{\textcolor{blue}{\emph{#1}} }

@@

\dropcap{D}omesticated plant species evolve in a unique fashion
compared to their wild relatives \textcolor{red}{(ref here)}. This
results from both the anthropomorphic nature of selection on
domesticates as well as the characteristics of the domestication
bottleneck that they usually experience \textcolor{red}{(ref here)}.

>>>>

\documentclass{pnastwo}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
%\usepackage{hyperref}
\newcommand{\jri}[1]{\textcolor{blue}{\emph{#1}} }

@@

\dropcap{D}omesticated plant species evolve in a unique fashion
compared to their wild relatives \textcolor{red}{(ref here)}. This
is a result of both the anthropomorphic nature of selection on
domesticates \cite{purugganan2009} as well as the demographic characteristics of the domestication
bottleneck that they tend to have experienced
\cite{ross2007}. However, the
complex interplay between selective pressures and demographic limitations in
domesticated species is not well understood. Despite the fact that,
researchers have searched the genomes of several species for evidence
of positive selection during domestication
\textcolor{red}{(citations here)}, these types of studies tend to focus on
identifying or mapping particular genes or regions that play an
important role in phenotypic evolution. Our knowledge regarding the impacts of demography and
selection have on whole-genome patterns of genetic variability therefore remain limited.
